\documentclass{resume} % Use the custom resume.cls style
\usepackage[none]{hyphenat}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,      
  urlcolor=blue,
  pdftitle={Nguyen-Phuc Tran's Resume},
  pdfpagemode=UseOutlines,
  }

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Nguyen-Phuc (Phill) Tran}
\email{phuctranse@gmail.com}
\phone{(438)-xxx-xxx}
\address{Montréal, QC, Canada} % \\ (open to relocation)}
\linkedin{linkedin.com/in/phuc-tran-mtl}
\github{github.com/nerostamas}


\begin{document}
%%%
%%%
%%%
\begin{rSection}{EXPERIENCES}
  \begin{rWork}{Research Consultant}{Ericsson Inc, Montreal}{Aug. 2023 - Present}
    \item Research and design a root cause analysis framework leveraging Python, Generative AI (specifically Large Language Models) to support critical network missions.
    \item Collaborated with team of domain experts, published 3+ internal documents and codes; one patent, 2 conference papers and 1 journal paper.
  \end{rWork}
  %
  \begin{rWork}{Research Consultant}{Ciena Inc, Montreal}{Sep. 2021 - Jul. 2023}
    \item Maintain and develop a 5G/B5G network slicing simulation utilizing C++ and Python along with Omnet++.
    \item Research and implement AI-driven algorithms for the service assurance to optimize network resources up to 54.85\% and reduce operating costs.
    \item Collaborated with technical experts, transferred knowledge and codes; 1 conference paper and 1 journal paper.
  \end{rWork}
  %
  \begin{rWork}{Senior full stack developer}{Egopulse \& Silentium VN, HCM}{Aug. 2018 - Jun. 2021}
    \item  Collaborated with a team of engineers to design, develop, test, deploy, and upgrade a microservices-based solution to ensure scalability and reliability for doctor–patient communication and clinic administration.
    \item Ensured continuous integration and deployment (CI/CD) remained operational by designing comprehensive test plans for new features and maintaining up-to-date unit tests, system tests, and end-to-end test scenarios.
    \item Performed code reviews to assist team members in minimizing code-related issues and ensuring adherence to coding standards and best practices.
    \item Assisted new team members in onboarding and becoming familiar with our software systems and development workflow.
    \item Tech stack: Docker, Java, GoLang, NodeJs, ReactJs, ReactNative, Python, Playwright, Mongodb, Message-Queue.
  \end{rWork}
  %
  \begin{rWork}{Software Developer}{DEK Technologies, HCM}{Jun. 2017 - Aug. 2018}
    \item Develop and maintain core middleware for high availability framework based on the Open-SAF architecture for Ericsson network using C++, Python, Java and Bash.
    \item Participate in code reviews and provide feedback.
    \item Integrate core middleware on different cloud environments.
    \item Participate in automated build and deployment processes.
    \item Support the release activities and documentation.
    \item Tech stack: C++, Python, Bash, Jenkin, Java, Docker.
  \end{rWork}
\end{rSection}
\begin{rSection}{EDUCATION}
\begin{rSchool}{Concordia University, Montreal}
  {\textbf{Fall 2021} - \textbf{Present}}
  {Ph.D. in Computer Science}
  {GPA: x/x}
  {Awards: Concordia International Tuition Award of Excellence, INNOV-R and NSERC research fellowship (2023-2025), Mitacs research fellowship (2021-2023), Concordia FRS bursaries.}
\end{rSchool}
%
\begin{rSchool}{University of Information
Technology - VNUHCM}
  {\textbf{Fall 2017} - \textbf{Fall 2020}}
  {Master of science in Computer Science}
  {GPA: x/x}
  {} \vspace{-3ex}
\end{rSchool}
%
\begin{rSchool}{Dong Nai Technology University}
  {\textbf{Fall 2013} - \textbf{Summer 2017}}
  {Bachelor of Engineering in Information Technology}
  {GPA: x/x}
  {Awards: 1st prize of Vietnam Maker Contest with Intel Galileo 2nd, Medal of Creative from Ho Chi Minh Communist Youth Union, 2016 Korean Government Sponsorship Summer Program for ASEAN Countries Science and Engineering Students}
\end{rSchool}
\end{rSection}
%%%
%%%
%%%
% \break

\begin{rSection}{SKILLS}
\textbf{Languages:} Python, Java, JavaScript/TypeScript, GoLang, SQL, NoSQL, C/C++, \LaTeX, Bash, HTML/CSS.

\textbf{Frameworks:} Micronaut, ReactJS, ReactNative, NodeJs, Playwright, MFC, Pandas, Tensorflow, Numpy, Scikit-learn, Git, Docker, Gitlab CI/CD, Jenkins, MySQL, Redis, MongoDB.

\textbf{Natural Languages:} English (fluent), French (intermediate), Vietnamese (native)

\end{rSection}
%%%
%%%
%%%
\end{document}
